---
title: "305 Final"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(tidyr)
library(dplyr)
library(kableExtra)
# Loading in the cleaned survey Data
setwd("D:/sta305")
survey_data <- read_csv("305_data1.csv")
attach(survey_data)

```


*Code and data supporting this analysis is available at:* \
https://github.com/leizikun/The-Prediction-of-2020-U.S.-Presidential-Election.git

|     We are interested in predicting the popular vote outcome of the 2020 U.S. presidential election (Dassonneville & Tien, 2020). In this report, we used post-stratification analysis based on a logistic regression model to predict the result of the U.S. Presidential Election in 2020. The result suggests that 36.1% of voters are in favor of voting for Donald Trump.

# Model

## Model Specifics



```{r}
boil <- within(survey_data, Treatment<-paste(Drink_type,Heating_level))
with(boil,tapply(Time_in_seconds,Treatment,mean))
boxplot(Time_in_seconds~Treatment,data=boil)
```


```{r, include=TRUE}
# Creating the Model
model1 <- lm(Time_in_seconds ~ Treatment, data=boil)
anova(model1)
```



















